2H qSIP Calculations

### 2022-03-16 qSIP_calculations.Rmd
added F_0 uncertainty

```{r}
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  # Don't want our standard compounds to be used for generation time calculations! x_x
  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
  left_join(F_L_2F, by = "terrain")
```

>>>>

## Separate analytes and standards

```{r}
# Analytes
peaks_mapped_with_zeros_analytes <- peaks_mapped_with_zeros_FID %>% 
  # Don't want our standard compounds to be used for generation time calculations! x_x
  filter(str_detect(compound, "STD", negate = TRUE)) %>% 
  left_join(F_L_2F, by = "terrain")

# Standards
peaks_mapped_with_zeros_standards<- peaks_mapped_with_zeros_FID %>% 
  filter(str_detect(compound, "STD"))

# 23:0 and 21:0 PC standard errors at inc time zero
# Determines our standard error in FAME measurements at F_0
sF_0 <- peaks_mapped_with_zeros_standards %>% 
  # Select only 21 and 23 PC standards at initial time point
  filter(compound %in% c("21:0 (STD)", "23:0 (STD)"),
         inc_time_d == 0) %>%
  group_by(compound) %>% 
  summarize(F_0_at2H_mn = mean(at2H),
            F_0_at2H_se = sd(at2H))
